---
title: "Exploratory data analysis"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type= "text/css">

. figure {
   margin-top: 25px;
   margin-bottom: 100px;
}

table {
    margin-top: 10px;
    margin-bottom: 25px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
```

```{r library}
library(here)
library(tidyverse)
library(labelled)
library(ggplot2)
library(ggforce)
library(gtsummary)
library(survminer)
library(survival)
theme_set(theme_classic())
theme_gtsummary_compact()
```

```{r load}
path <- fs::path("", "Volumes", "Peres_Research", "AACES2", "Analgesic medications and survival")
analgesics <-
  read_csv(paste0(here::here(), "/Cleaned analgesics medication data_02152024.csv"))
```

```{r Labeling}
var_label(analgesics) <- list(refage = "Patient age", 
                         stage = "Clinical stage", histotype2 = "Histotype", 
                         BMI_recent = "BMI (recent)", bmicat = "BMI categories", 
                         menopause = "Menopause", smokcurrent2 = "Smoking status", 
                         neoadj_treat = "Received neoadjuvant", 
                         dblk_imp = "debulking status (imputed)", 
                         NEW_dblkstat_treat_CA125 = "debulking status", 
                         CCI_new = "CCI", CCI_new_Cat = "CCI categories",
                         aspirin = "Aspirin use",
                         aspirin_duration = "Aspirin duration (months)", 
                         aspirin_freq = "Aspirin frequency (Number of days per month)", 
                         aspirin_ind = "Aspirin indication",
                         nsaid = "Non-aspirin NSAID use", 
                         nsaid_duration = "Non-aspirin NSAID duration (months)", 
                         nsaid_freq = "Non-aspirin NSAID frequency (Number of days per month)", 
                         nsaid_ind = "Non-aspirin NSAID indication",
                         aceta = "Acetaminophen use", 
                         acetaminophen_duration = "Acetaminophen duration (months)", 
                         acetaminophen_freq = "Acetaminophen frequency (Number of days per month)", 
                         aceta_ind = "Acetaminophen indication")

```

# 1. Clinical table
```{r}
analgesics %>% 
  select(refage, stage, histotype, histotype2,
         BMI_recent, bmicat, menopause, smokcurrent2, 
         neoadj_treat, dblk_imp, NEW_dblkstat_treat_CA125, 
         CCI_new, CCI_new_Cat) %>% 
  tbl_summary(type = list(
    neoadj_treat ~ "categorical"
  )) %>% 
  bold_labels() %>% add_stat_label()
```

# 2. Analgesics table
```{r}
analgesics %>% 
  select(aspirin, aspirin_duration, aspirin_freq, aspirin_ind,
         nsaid, nsaid_duration, nsaid_freq, nsaid_ind,
         aceta, acetaminophen_duration, acetaminophen_freq, aceta_ind) %>% 
  tbl_summary(type = list(
    c(aspirin, nsaid, aceta) ~ "categorical"
  )) %>% 
  bold_labels() %>% add_stat_label()
```

# 3. Plots
### Aspirin
```{r}
analgesics %>% 
  select(aspirin_duration) %>% 
  group_by(aspirin_duration) %>% 
  mutate(n = n()) %>% 
  ungroup() %>% 
  ggplot()+
  geom_area(aes(x = aspirin_duration, y = n), 
            alpha = 0.5, fill = "grey")+
  geom_bar(data = analgesics, aes(x = aspirin_duration), 
           width = 0.5, fill = "darkblue")+
  facet_zoom(ylim = c(0, 10))

analgesics %>% 
  select(aspirin_freq) %>% 
  group_by(aspirin_freq) %>% 
  mutate(n = n()) %>% 
  ungroup() %>% 
  ggplot()+
  geom_area(aes(x = aspirin_freq, y = n),
            alpha = 0.5, fill = "grey")+
  geom_bar(data = analgesics, aes(x = aspirin_freq), 
           width = 0.1, fill = "darkblue")+
  facet_zoom(ylim = c(0, 10))
```

### NSAID
```{r}
analgesics %>% 
  select(nsaid_duration) %>% 
  group_by(nsaid_duration) %>% 
  mutate(n = n()) %>% 
  ungroup() %>% 
  ggplot()+
  geom_area(aes(x = nsaid_duration, y = n), 
            alpha = 0.5, fill = "grey")+
  geom_bar(data = analgesics, aes(x = nsaid_duration), 
           width = 0.5, fill = "darkblue")+
  facet_zoom(ylim = c(0, 10))

analgesics %>% 
  select(nsaid_freq) %>% 
  group_by(nsaid_freq) %>% 
  mutate(n = n()) %>% 
  ungroup() %>% 
  ggplot()+
  geom_area(aes(x = nsaid_freq, y = n), 
            alpha = 0.5, fill = "grey")+
  geom_bar(data = analgesics, aes(x = nsaid_freq), 
           width = 0.1, fill = "darkblue")+
  facet_zoom(ylim = c(0, 10))
```

### Acetaminophen
```{r}
analgesics %>% 
  select(acetaminophen_duration) %>% 
  group_by(acetaminophen_duration) %>% 
  mutate(n = n()) %>% 
  ungroup() %>% 
  ggplot()+
  geom_area(aes(x = acetaminophen_duration, y = n), 
            alpha = 0.5, fill = "grey")+
  geom_bar(data = analgesics, aes(x = acetaminophen_duration), 
           width = 0.5, fill = "darkblue")+
  facet_zoom(ylim = c(0, 10))

analgesics %>% 
  select(acetaminophen_freq) %>% 
  group_by(acetaminophen_freq) %>% 
  mutate(n = n()) %>% 
  ungroup() %>% 
  ggplot()+
  geom_area(aes(x = acetaminophen_freq, y = n), 
            alpha = 0.5, fill = "grey")+
  geom_bar(data = analgesics, aes(x = acetaminophen_freq), 
           width = 0.1, fill = "darkblue")+
  facet_zoom(ylim = c(0, 10))
```

## Using Never/Ever group
### How do the "Ever" groups overlap?
How many patients received none of the analgesics? `r analgesics %>% filter(aspirin == "No" & nsaid == "No" & aceta == "No") %>% nrow()`
```{r VennDiagram}
library(VennDiagram)

aspirin <- analgesics %>% filter(aspirin == "Yes")
nsaid <- analgesics %>% filter(nsaid == "Yes")
aceta <- analgesics %>% filter(aceta == "Yes")

# venn.diagram(
#   x = list(aspirin$suid, 
#            nsaid$suid,
#            aceta$suid
#            ),
#   category.names = c("Aspirin" , "NSAID", "Acetaminophen"),
#   filename = 'Patients with Analgesics.png',
#   disable.logging = TRUE,
#   output=TRUE,
#   
#   # Output features
#   imagetype="png" ,
#   height = 1000 , 
#   width = 1000 , 
#   resolution = 300,
#   compression = "lzw",
#   
#   # Circles
#   lwd = 2,
#   lty = 'blank',
#   fill = c(viridis::cividis(3)),
#   margin = 0.2,
#   
#   # Numbers
#   cex = .6,
#   fontface = "bold",
#   fontfamily = "sans",
#   # cat.pos = c(90, 0, 0),
#   cat.dist = c(0.08, 0.08, 0.04)
#   # ext.percent = 2
#   #ext.percent = 5
# )
knitr::include_graphics(paste0(here::here(), "/Patients with Analgesics.png"))
```

## 4. Tables by analgesics
```{r}
analgesics %>% 
  select(refage, stage, histotype, histotype2,
         BMI_recent, bmicat, menopause, smokcurrent2, 
         neoadj_treat, dblk_imp, NEW_dblkstat_treat_CA125, 
         CCI_new, CCI_new_Cat,
         aspirin, aspirin_duration, aspirin_freq, aspirin_ind,
         nsaid, nsaid_duration, nsaid_freq, nsaid_ind,
         aceta, acetaminophen_duration, acetaminophen_freq, aceta_ind) %>% 
  tbl_summary(by = aspirin,
              type = list(
    c(neoadj_treat, aspirin, nsaid, aceta) ~ "categorical"
  )) %>% 
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% bold_p(t = 0.05) %>% 
  modify_caption("**By Aspirin Use** (N = {N})")

analgesics %>% 
  select(refage, stage, histotype, histotype2,
         BMI_recent, bmicat, menopause, smokcurrent2, 
         neoadj_treat, dblk_imp, NEW_dblkstat_treat_CA125, 
         CCI_new, CCI_new_Cat,
         aspirin, aspirin_duration, aspirin_freq, aspirin_ind,
         nsaid, nsaid_duration, nsaid_freq, nsaid_ind,
         aceta, acetaminophen_duration, acetaminophen_freq, aceta_ind) %>% 
  tbl_summary(by = nsaid,
              type = list(
    c(neoadj_treat, aspirin, nsaid, aceta) ~ "categorical"
  )) %>% 
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% bold_p(t = 0.05) %>% 
  modify_caption("**By NSAID Use** (N = {N})")

analgesics %>% 
  select(refage, stage, histotype, histotype2,
         BMI_recent, bmicat, menopause, smokcurrent2, 
         neoadj_treat, dblk_imp, NEW_dblkstat_treat_CA125, 
         CCI_new, CCI_new_Cat,
         aspirin, aspirin_duration, aspirin_freq, aspirin_ind,
         nsaid, nsaid_duration, nsaid_freq, nsaid_ind,
         aceta, acetaminophen_duration, acetaminophen_freq, aceta_ind) %>% 
  tbl_summary(by = aceta,
              type = list(
    c(neoadj_treat, aspirin, nsaid, aceta) ~ "categorical"
  )) %>% 
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% bold_p(t = 0.05) %>% 
  modify_caption("**By Acetaminophen Use** (N = {N})")
```

## 5. Survival
### KM

<div class = "row">
<div class = "col-md-4">
```{r KM, fig.height = 8}
ggsurvplot(survfit(Surv(os_time, os_event) ~ aspirin, 
                   data=analgesics),
           title = "OS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))

```
</div>

<div class = "col-md-4">
```{r fig.height = 8}
ggsurvplot(survfit(Surv(os_time, os_event) ~ nsaid, 
                   data=analgesics),
           title = "OS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))
```
</div>

<div class = "col-md-4">
```{r fig.height = 8}
ggsurvplot(survfit(Surv(os_time, os_event) ~ aceta, 
                   data=analgesics),
           title = "OS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))
```
</div>
</div>

### Model 1 - adjust for age, study site, stage, and histotype
```{r}
tbl1 <- analgesics %>% select(os_event, os_time,
                              aspirin, nsaid, aceta,
                              refage, site, stage, 
                              histotype2) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = analgesics$os_time,
                             event = analgesics$os_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl2 <- coxph(Surv(time = analgesics$os_time, 
                   event = analgesics$os_event) ~ aspirin + nsaid + aceta + refage + site + stage + histotype2,
              data = analgesics)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```

PH assumption
```{r}
coxph(Surv(time = analgesics$os_time, 
                   event = analgesics$os_event) ~ aspirin + nsaid + aceta + refage + site + stage + histotype2,
              data = analgesics)  %>%
  cox.zph()
```

### Model 2 - + bmicat, smokcurrent2, CCI_new_Cat (could use continuous + need to ask Alicia) - I don't have physical activity
```{r}
tbl1 <- analgesics %>% select(os_event, os_time,
                              aspirin, nsaid, aceta,
                              refage, site, stage, 
                              histotype2, 
                              bmicat, smokcurrent2, CCI_new_Cat) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = analgesics$os_time,
                             event = analgesics$os_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl2 <- coxph(Surv(time = analgesics$os_time, 
                   event = analgesics$os_event) ~ aspirin + nsaid + aceta + refage + site + stage + histotype2 +
                bmicat + smokcurrent2 + CCI_new_Cat,
              data = analgesics)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```

PH assumption
```{r}
coxph(Surv(time = analgesics$os_time, 
                   event = analgesics$os_event) ~ aspirin + nsaid + aceta + refage + site + stage + histotype2 +
                bmicat + smokcurrent2 + CCI_new_Cat,
              data = analgesics) %>%
  cox.zph()
```

### Model 3 - + indication (make group maybe no use, heart disease and others)


# 4. Using a cut point - to come

# 5. Stratified analysis by histotype

# 6. Sensitivity analysis adjusting for treatment 





