---
title: "Additional analyses"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    toc_depth : 4
    theme: united
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type= "text/css">

. figure {
   margin-top: 25px;
   margin-bottom: 100px;
}

table {
    margin-top: 10px;
    margin-bottom: 25px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
```

```{r library}
library(here)
library(tidyverse)
library(labelled)
library(ggplot2)
library(ggforce)
library(gtsummary)
library(survminer)
library(survival)
theme_set(theme_classic())
theme_gtsummary_compact()
```

```{r load}
path <- fs::path("", "Volumes", "Peres_Research", "AACES2", "Analgesic medications and survival")
analgesics <-
  read_rds(paste0(here::here(), "/Cleaned imputed analgesics medication data_phase1 w income insurance education_05302024.rds")) %>% 
  rename(imp_debulking = imp_NEW_dblkstat_treat_CA125)
```

```{r Labeling imputed data}
var_label(analgesics) <- list(refage = "Patient age", 
                         stage = "Clinical stage", imp_stage = "Clinical stage*", 
                         histotype2 = "Histotype", imp_histotype2 = "Histotype*", 
                         BMI_recent = "BMI (recent)", BMI_recent_grp = "BMI categories", 
                         imp_BMI_recent_grp = "BMI categories*", 
                         ins2 = "Insurance",
                         private_insurance = "Private insurance", 
                         imp_private_insurance = "Private insurance*", 
                         medicare_insurance = "Medicare insurance",
                         imp_medicare_insurance = "Medicare insurance*",
                         medicaid_insurance = "Medicaid insurance",
                         imp_medicaid_insurance = "Medicaid insurance*",
                         menopause = "Menopause", imp_menopause = "Menopause*",
                         education = "Education", imp_education = "Education*",
                         smokcurrent2 = "Smoking status", 
                         paga = "Physical activity", imp_paga = "Physical activity*",
                         neoadj_treat = "Received neoadjuvant", 
                         imp_neoadj_treat = "Received neoadjuvant*", 
                         imp_debulking = "Debulking status*", 
                         NEW_dblkstat_treat_CA125 = "Debulking status", 
                         CCI_new = "CCI", CCI_new_Cat = "CCI categories",
                         imp_CCI_new_Cat = "CCI categories*",
                         aspirin = "Aspirin use",
                         aspirin_duration = "Aspirin duration (months)", 
                         aspirin_duration_cat = "Aspirin duration",
                         aspirin_duration_for_users = "Aspirin duration for users (months)",
                         aspirin_freq = "Aspirin frequency (Number of days per month)", 
                         aspirin_freq_cat = "Aspirin frequency",
                         aspirin_freq_for_users = "Aspirin frequency for users (Number of days per month)", 
                         aspirin_ind_init = "Aspirin indication (initial categories)",
                         aspirin_ind = "Aspirin indication",
                         nsaid = "Non-aspirin NSAID use", 
                         nsaid_duration = "Non-aspirin NSAID duration (months)", 
                         nsaid_duration_cat = "Non-aspirin NSAID duration",
                         nsaid_duration_for_users = "Non-aspirin NSAID duration for users (months)", 
                         nsaid_freq = "Non-aspirin NSAID frequency (Number of days per month)", 
                         nsaid_freq_cat = "Non-aspirin NSAID frequency",
                         nsaid_freq_for_users = "Non-aspirin NSAID frequency for users (Number of days per month)", 
                         nsaid_ind_init = "Non-aspirin NSAID indication (initial categories)",
                         nsaid_ind = "Non-aspirin NSAID indication",
                         aceta = "Acetaminophen use", 
                         acetaminophen_duration = "Acetaminophen duration (months)", 
                         acetaminophen_duration_cat = "Acetaminophen duration",
                         acetaminophen_duration_for_users = "Acetaminophen duration for users (months)", 
                         acetaminophen_freq = "Acetaminophen frequency (Number of days per month)", 
                         acetaminophen_freq_cat = "Acetaminophen frequency",
                         acetaminophen_freq_for_users = "Acetaminophen frequency for users (Number of days per month)", 
                         aceta_ind_init = "Acetaminophen indication (initial categories)",
                         aceta_ind = "Acetaminophen indication",
                         site_2 = "Study site")
```

# I. HR - Stratified by histotype - Imputed data

## 1. HGSC/carcinosarcoma
```{r}
analgenics_HGSC <- analgesics %>%
  filter(imp_histotype2 == "HGSC/carcinosarcoma")
```

### a. Yes/No users
```{r}
model_1 <- coxph(Surv(time = analgenics_HGSC$os_time, 
                   event = analgenics_HGSC$os_event) ~ aspirin + nsaid + aceta + refage + site_2 + imp_stage,
              data = analgenics_HGSC)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_2 <- coxph(Surv(time = analgenics_HGSC$os_time, 
                      event = analgenics_HGSC$os_event) ~ aspirin + nsaid + aceta + refage + site_2 + imp_stage + 
                   imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance,
                 data = analgenics_HGSC)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_3 <- coxph(Surv(time = analgenics_HGSC$os_time, 
                   event = analgenics_HGSC$os_event) ~ aspirin + nsaid + aceta + refage + site_2 + imp_stage + 
                  imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance + 
                  imp_debulking,
              data = analgenics_HGSC)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

tbl_merge(list(model_1, model_2, model_3), tab_spanner = c("**Primary**", "**+ counfounders**", "**Fully adjusted**"))
```

### b. cut-points - duration
```{r}
model_1 <- coxph(Surv(time = analgenics_HGSC$os_time, 
                   event = analgenics_HGSC$os_event) ~ aspirin_duration_cat + nsaid_duration_cat + acetaminophen_duration_cat + 
                refage + site_2 + imp_stage,
              data = analgenics_HGSC)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_2 <- coxph(Surv(time = analgenics_HGSC$os_time, 
                   event = analgenics_HGSC$os_event) ~ aspirin_duration_cat + nsaid_duration_cat + acetaminophen_duration_cat +
                refage + site_2 + imp_stage +
                imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance,
              data = analgenics_HGSC)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_3 <- coxph(Surv(time = analgenics_HGSC$os_time, 
                   event = analgenics_HGSC$os_event) ~ aspirin_duration_cat + nsaid_duration_cat + acetaminophen_duration_cat +
                refage + site_2 + imp_stage +
                imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance + 
                  imp_debulking,
              data = analgenics_HGSC)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

tbl_merge(list(model_1, model_2, model_3), 
                          tab_spanner = c("**Primary**", "**+ counfounders**", "**Fully adjusted**"))
```

### c. cut-points - frequency
```{r}
model_1 <- coxph(Surv(time = analgenics_HGSC$os_time, 
                   event = analgenics_HGSC$os_event) ~ aspirin_freq_cat + nsaid_freq_cat + acetaminophen_freq_cat + 
                refage + site_2 + imp_stage,
              data = analgenics_HGSC)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_2 <- coxph(Surv(time = analgenics_HGSC$os_time, 
                   event = analgenics_HGSC$os_event) ~ aspirin_freq_cat + nsaid_freq_cat + acetaminophen_freq_cat + 
                refage + site_2 + imp_stage +
                imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance,
              data = analgenics_HGSC)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_3 <- coxph(Surv(time = analgenics_HGSC$os_time, 
                   event = analgenics_HGSC$os_event) ~ aspirin_freq_cat + nsaid_freq_cat + acetaminophen_freq_cat + 
                refage + site_2 + imp_stage +
                imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance + 
                  imp_debulking,
              data = analgenics_HGSC)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

tbl_merge(list(model_1, model_2, model_3), 
                           tab_spanner = c("**Primary**", "**+ counfounders**", "**Fully adjusted**"))
```

## 2. Not HGSC/carcinosarcoma
```{r}
analgenics_notHGSC <- analgesics %>%
  filter(imp_histotype2 == "not HGSC/carcinosarcoma")
```

### a. Yes/No users
```{r}
model_1 <- coxph(Surv(time = analgenics_notHGSC$os_time, 
                   event = analgenics_notHGSC$os_event) ~ aspirin + nsaid + aceta + refage + site_2 + imp_stage,
              data = analgenics_notHGSC)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_2 <- coxph(Surv(time = analgenics_notHGSC$os_time, 
                      event = analgenics_notHGSC$os_event) ~ aspirin + nsaid + aceta + refage + site_2 + imp_stage + 
                   imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance,
                 data = analgenics_notHGSC)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_3 <- coxph(Surv(time = analgenics_notHGSC$os_time, 
                   event = analgenics_notHGSC$os_event) ~ aspirin + nsaid + aceta + refage + site_2 + imp_stage + 
                  imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance + 
                  imp_debulking,
              data = analgenics_notHGSC)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

tbl_merge(list(model_1, model_2, model_3), tab_spanner = c("**Primary**", "**+ counfounders**", "**Fully adjusted**"))
```

### b. cut-points - duration
```{r}
model_1 <- coxph(Surv(time = analgenics_notHGSC$os_time, 
                   event = analgenics_notHGSC$os_event) ~ aspirin_duration_cat + nsaid_duration_cat + acetaminophen_duration_cat + 
                refage + site_2 + imp_stage,
              data = analgenics_notHGSC)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_2 <- coxph(Surv(time = analgenics_notHGSC$os_time, 
                   event = analgenics_notHGSC$os_event) ~ aspirin_duration_cat + nsaid_duration_cat + acetaminophen_duration_cat +
                refage + site_2 + imp_stage +
                imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance,
              data = analgenics_notHGSC)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_3 <- coxph(Surv(time = analgenics_notHGSC$os_time, 
                   event = analgenics_notHGSC$os_event) ~ aspirin_duration_cat + nsaid_duration_cat + acetaminophen_duration_cat +
                refage + site_2 + imp_stage +
                imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance + 
                  imp_debulking,
              data = analgenics_notHGSC)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

tbl_merge(list(model_1, model_2, model_3), 
                          tab_spanner = c("**Primary**", "**+ counfounders**", "**Fully adjusted**"))
```

### c. cut-points - frequency
NA
```{r}
# model_1 <- coxph(Surv(time = analgenics_notHGSC$os_time, 
#                    event = analgenics_notHGSC$os_event) ~ aspirin_freq_cat + nsaid_freq_cat + acetaminophen_freq_cat + 
#                 refage + site_2 + imp_stage,
#               data = analgenics_notHGSC)  %>% 
#   tbl_regression(exponentiate = TRUE) %>% 
#   bold_labels() %>% italicize_levels() %>% 
#   bold_p(t = .05) %>% 
#   add_nevent(location = "level") %>% add_n(location = "level")
# 
# model_2 <- coxph(Surv(time = analgenics_notHGSC$os_time, 
#                    event = analgenics_notHGSC$os_event) ~ aspirin_freq_cat + nsaid_freq_cat + acetaminophen_freq_cat + 
#                 refage + site_2 + imp_stage +
#                 imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
#                    imp_medicaid_insurance,
#               data = analgenics_notHGSC)  %>% 
#   tbl_regression(exponentiate = TRUE) %>% 
#   bold_p(t = .05) %>% 
#   add_nevent(location = "level") %>% add_n(location = "level")
# 
# model_3 <- coxph(Surv(time = analgenics_notHGSC$os_time, 
#                    event = analgenics_notHGSC$os_event) ~ aspirin_freq_cat + nsaid_freq_cat + acetaminophen_freq_cat + 
#                 refage + site_2 + imp_stage +
#                 imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
#                    imp_medicaid_insurance + 
#                   imp_debulking,
#               data = analgenics_notHGSC)  %>% 
#   tbl_regression(exponentiate = TRUE) %>% 
#   bold_p(t = .05) %>% 
#   add_nevent(location = "level") %>% add_n(location = "level")
# 
# tbl_merge(list(model_1, model_2, model_3), 
#                            tab_spanner = c("**Primary**", "**+ counfounders**", "**Fully adjusted**"))
```










# II. HR - Stratified by CCI - Imputed data

## 1. CCI score is 0
```{r}
analgenics_CCI_0 <- analgesics %>%
  filter(imp_CCI_new_Cat == "CCI score is 0")
```

### a. Yes/No users
```{r}
model_1 <- coxph(Surv(time = analgenics_CCI_0$os_time, 
                   event = analgenics_CCI_0$os_event) ~ aspirin + nsaid + aceta + refage + site_2 + imp_stage + 
                strata(imp_histotype2),
              data = analgenics_CCI_0)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_2 <- coxph(Surv(time = analgenics_CCI_0$os_time, 
                      event = analgenics_CCI_0$os_event) ~ aspirin + nsaid + aceta + refage + site_2 + imp_stage + 
                strata(imp_histotype2) + 
                   imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance,
                 data = analgenics_CCI_0)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_3 <- coxph(Surv(time = analgenics_CCI_0$os_time, 
                   event = analgenics_CCI_0$os_event) ~ aspirin + nsaid + aceta + refage + site_2 + imp_stage + 
                strata(imp_histotype2) + 
                  imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance + 
                  imp_debulking,
              data = analgenics_CCI_0)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

tbl_merge(list(model_1, model_2, model_3), tab_spanner = c("**Primary**", "**+ counfounders**", "**Fully adjusted**"))
```

### b. cut-points - duration
```{r}
model_1 <- coxph(Surv(time = analgenics_CCI_0$os_time, 
                   event = analgenics_CCI_0$os_event) ~ aspirin_duration_cat + nsaid_duration_cat + acetaminophen_duration_cat + 
                refage + site_2 + imp_stage + 
                strata(imp_histotype2),
              data = analgenics_CCI_0)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_2 <- coxph(Surv(time = analgenics_CCI_0$os_time, 
                   event = analgenics_CCI_0$os_event) ~ aspirin_duration_cat + nsaid_duration_cat + acetaminophen_duration_cat +
                refage + site_2 + imp_stage + 
                strata(imp_histotype2) +
                imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance,
              data = analgenics_CCI_0)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_3 <- coxph(Surv(time = analgenics_CCI_0$os_time, 
                   event = analgenics_CCI_0$os_event) ~ aspirin_duration_cat + nsaid_duration_cat + acetaminophen_duration_cat +
                refage + site_2 + imp_stage + 
                strata(imp_histotype2) +
                imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance + 
                  imp_debulking,
              data = analgenics_CCI_0)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

tbl_merge(list(model_1, model_2, model_3), 
                          tab_spanner = c("**Primary**", "**+ counfounders**", "**Fully adjusted**"))
```

### c. cut-points - frequency
```{r}
model_1 <- coxph(Surv(time = analgenics_CCI_0$os_time, 
                   event = analgenics_CCI_0$os_event) ~ aspirin_freq_cat + nsaid_freq_cat + acetaminophen_freq_cat + 
                refage + site_2 + imp_stage + 
                strata(imp_histotype2),
              data = analgenics_CCI_0)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_2 <- coxph(Surv(time = analgenics_CCI_0$os_time, 
                   event = analgenics_CCI_0$os_event) ~ aspirin_freq_cat + nsaid_freq_cat + acetaminophen_freq_cat + 
                refage + site_2 + imp_stage + 
                strata(imp_histotype2) +
                imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance,
              data = analgenics_CCI_0)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_3 <- coxph(Surv(time = analgenics_CCI_0$os_time, 
                   event = analgenics_CCI_0$os_event) ~ aspirin_freq_cat + nsaid_freq_cat + acetaminophen_freq_cat + 
                refage + site_2 + imp_stage + 
                strata(imp_histotype2) +
                imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance + 
                  imp_debulking,
              data = analgenics_CCI_0)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

tbl_merge(list(model_1, model_2, model_3), 
                           tab_spanner = c("**Primary**", "**+ counfounders**", "**Fully adjusted**"))
```

## 1. CCI score ≥ 1
```{r}
analgenics_CCI_other <- analgesics %>%
  filter(imp_CCI_new_Cat != "CCI score is 0")
```

### a. Yes/No users
```{r}
model_1 <- coxph(Surv(time = analgenics_CCI_other$os_time, 
                   event = analgenics_CCI_other$os_event) ~ aspirin + nsaid + aceta + refage + site_2 + imp_stage + 
                strata(imp_histotype2),
              data = analgenics_CCI_other)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_2 <- coxph(Surv(time = analgenics_CCI_other$os_time, 
                      event = analgenics_CCI_other$os_event) ~ aspirin + nsaid + aceta + refage + site_2 + imp_stage + 
                strata(imp_histotype2) + 
                   imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance,
                 data = analgenics_CCI_other)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_3 <- coxph(Surv(time = analgenics_CCI_other$os_time, 
                   event = analgenics_CCI_other$os_event) ~ aspirin + nsaid + aceta + refage + site_2 + imp_stage + 
                strata(imp_histotype2) + 
                  imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance + 
                  imp_debulking,
              data = analgenics_CCI_other)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

tbl_merge(list(model_1, model_2, model_3), tab_spanner = c("**Primary**", "**+ counfounders**", "**Fully adjusted**"))
```

### b. cut-points - duration
```{r}
model_1 <- coxph(Surv(time = analgenics_CCI_other$os_time, 
                   event = analgenics_CCI_other$os_event) ~ aspirin_duration_cat + nsaid_duration_cat + acetaminophen_duration_cat + 
                refage + site_2 + imp_stage + 
                strata(imp_histotype2),
              data = analgenics_CCI_other)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_2 <- coxph(Surv(time = analgenics_CCI_other$os_time, 
                   event = analgenics_CCI_other$os_event) ~ aspirin_duration_cat + nsaid_duration_cat + acetaminophen_duration_cat +
                refage + site_2 + imp_stage + 
                strata(imp_histotype2) +
                imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance,
              data = analgenics_CCI_other)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_3 <- coxph(Surv(time = analgenics_CCI_other$os_time, 
                   event = analgenics_CCI_other$os_event) ~ aspirin_duration_cat + nsaid_duration_cat + acetaminophen_duration_cat +
                refage + site_2 + imp_stage + 
                strata(imp_histotype2) +
                imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance + 
                  imp_debulking,
              data = analgenics_CCI_other)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

tbl_merge(list(model_1, model_2, model_3), 
                          tab_spanner = c("**Primary**", "**+ counfounders**", "**Fully adjusted**"))
```

### c. cut-points - frequency
```{r}
model_1 <- coxph(Surv(time = analgenics_CCI_other$os_time, 
                   event = analgenics_CCI_other$os_event) ~ aspirin_freq_cat + nsaid_freq_cat + acetaminophen_freq_cat + 
                refage + site_2 + imp_stage + 
                strata(imp_histotype2),
              data = analgenics_CCI_other)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_2 <- coxph(Surv(time = analgenics_CCI_other$os_time, 
                   event = analgenics_CCI_other$os_event) ~ aspirin_freq_cat + nsaid_freq_cat + acetaminophen_freq_cat + 
                refage + site_2 + imp_stage + 
                strata(imp_histotype2) +
                imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance,
              data = analgenics_CCI_other)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_3 <- coxph(Surv(time = analgenics_CCI_other$os_time, 
                   event = analgenics_CCI_other$os_event) ~ aspirin_freq_cat + nsaid_freq_cat + acetaminophen_freq_cat + 
                refage + site_2 + imp_stage + 
                strata(imp_histotype2) +
                imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance + 
                  imp_debulking,
              data = analgenics_CCI_other)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

tbl_merge(list(model_1, model_2, model_3), 
                           tab_spanner = c("**Primary**", "**+ counfounders**", "**Fully adjusted**"))
```

# II. HR - Complete cases
### a. Yes/No users
```{r}
model_2 <- coxph(Surv(time = analgesics$os_time, 
                   event = analgesics$os_event) ~ aspirin + nsaid + aceta + refage + site_2 + stage + 
                strata(histotype2) +
                CCI_new_Cat + BMI_recent_grp + private_insurance + medicare_insurance +
                   medicaid_insurance,
              data = analgesics)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
model_3 <- coxph(Surv(time = analgesics$os_time, 
                   event = analgesics$os_event) ~ aspirin + nsaid + aceta + refage + site_2 + stage + 
                strata(histotype2) +
                CCI_new_Cat + BMI_recent_grp + private_insurance + medicare_insurance +
                   medicaid_insurance + 
                  NEW_dblkstat_treat_CA125,
              data = analgesics)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(model_2, model_3), 
                           tab_spanner = c("**+ counfounders**", "**Fully adjusted**"))
```

### b. cut-points - duration
```{r}
model_2 <- coxph(Surv(time = analgesics$os_time, 
                   event = analgesics$os_event) ~ aspirin_duration_cat + nsaid_duration_cat + acetaminophen_duration_cat +
                   refage + site_2 + stage + 
                strata(histotype2) +
                CCI_new_Cat + BMI_recent_grp + private_insurance + medicare_insurance +
                   medicaid_insurance,
              data = analgesics)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
model_3 <- coxph(Surv(time = analgesics$os_time, 
                   event = analgesics$os_event) ~ aspirin_duration_cat + nsaid_duration_cat + acetaminophen_duration_cat +
                   refage + site_2 + stage + 
                strata(histotype2) +
                CCI_new_Cat + BMI_recent_grp + private_insurance + medicare_insurance +
                   medicaid_insurance + 
                  NEW_dblkstat_treat_CA125,
              data = analgesics)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(model_2, model_3), 
                           tab_spanner = c("**+ counfounders**", "**Fully adjusted**"))
```

### c. cut-points - frequency
```{r}
model_2 <- coxph(Surv(time = analgesics$os_time, 
                   event = analgesics$os_event) ~ aspirin_freq_cat + nsaid_freq_cat + acetaminophen_freq_cat + 
                   refage + site_2 + stage + 
                strata(histotype2) +
                CCI_new_Cat + BMI_recent_grp + private_insurance + medicare_insurance +
                   medicaid_insurance,
              data = analgesics)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
model_3 <- coxph(Surv(time = analgesics$os_time, 
                   event = analgesics$os_event) ~ aspirin_freq_cat + nsaid_freq_cat + acetaminophen_freq_cat +
                   refage + site_2 + stage + 
                strata(histotype2) +
                CCI_new_Cat + BMI_recent_grp + private_insurance + medicare_insurance +
                   medicaid_insurance + 
                  NEW_dblkstat_treat_CA125,
              data = analgesics)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(model_2, model_3), 
                           tab_spanner = c("**+ counfounders**", "**Fully adjusted**"))
```


# Heart and alchool
```{r}
analgesics <-
  read_rds(paste0(here::here(), "/analgesics data with heart kidney liver var for quick look 06262024.rds"))
```

```{r}
analgesics %>% 
  select(heart_trouble : wine_cat2) %>% 
  tbl_summary(type = list(
    c(heart_trouble, kidney_disease,
      liver_problems) ~ "categorical",
    c(liver_problems_age) ~ "continuous"),
    statistic=list(all_continuous() ~ "{median} ({min}, {max})"
    )) %>% 
  bold_labels() %>% add_stat_label()
```

```{r}
tbl1 <- analgesics %>% 
  select(heart_trouble : wine_cat2,
         aspirin) %>% 

  tbl_summary(by = aspirin,
              type = list(
    c(heart_trouble, kidney_disease,
      liver_problems) ~ "categorical",
    c(liver_problems_age) ~ "continuous"),
    statistic=list(all_continuous() ~ "{median} ({min}, {max})"
  )) %>% 
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% bold_p(t = 0.05)

tbl2 <- analgesics %>% 
  select(heart_trouble : wine_cat2,
         nsaid) %>% 

  tbl_summary(by = nsaid,
              type = list(
    c(heart_trouble, kidney_disease,
      liver_problems) ~ "categorical",
    c(liver_problems_age) ~ "continuous"),
    statistic=list(all_continuous() ~ "{median} ({min}, {max})"
  )) %>% 
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% bold_p(t = 0.05)

tbl3 <- analgesics %>% 
  select(heart_trouble : wine_cat2,
         aceta) %>% 

  tbl_summary(by = aceta,
              type = list(
    c(heart_trouble, kidney_disease,
      liver_problems) ~ "categorical",
    c(liver_problems_age) ~ "continuous"),
    statistic=list(all_continuous() ~ "{median} ({min}, {max})"
  )) %>% 
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% bold_p(t = 0.05)
```

```{r}
tbl_merge(list(tbl1, tbl2, tbl3), tab_spanner = c("**By Aspirin Use** (N = {N})",
                                                  "**By NSAID Use** (N = {N})",
                                                  "**By Acetaminophen Use** (N = {N})"))
```









