---
title: "Drug overlap and doses"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    toc_depth : 4
    theme: united
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type= "text/css">

. figure {
   margin-top: 25px;
   margin-bottom: 100px;
}

table {
    margin-top: 10px;
    margin-bottom: 25px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
```

```{r library}
library(here)
library(tidyverse)
library(labelled)
library(ggplot2)
library(ggforce)
library(gtsummary)
library(survminer)
library(survival)
theme_set(theme_classic())
theme_gtsummary_compact()
```

```{r load}
path <- fs::path("", "Volumes", "Peres_Research", "AACES2", "Analgesic medications and survival")
analgesics <-
  read_rds(paste0(here::here(), "/Cleaned imputed analgesics medication data_phase1 w income insurance education_05302024.rds")) %>% 
  rename(imp_debulking = imp_NEW_dblkstat_treat_CA125)
```

```{r Labeling imputed data}
var_label(analgesics) <- list(refage = "Patient age", 
                         stage = "Clinical stage", imp_stage = "Clinical stage*", 
                         histotype2 = "Histotype", imp_histotype2 = "Histotype*", 
                         BMI_recent = "BMI (recent)", BMI_recent_grp = "BMI categories", 
                         imp_BMI_recent_grp = "BMI categories*", 
                         ins2 = "Insurance",
                         private_insurance = "Private insurance", 
                         imp_private_insurance = "Private insurance*", 
                         medicare_insurance = "Medicare insurance",
                         imp_medicare_insurance = "Medicare insurance*",
                         medicaid_insurance = "Medicaid insurance",
                         imp_medicaid_insurance = "Medicaid insurance*",
                         menopause = "Menopause", imp_menopause = "Menopause*",
                         education = "Education", imp_education = "Education*",
                         smokcurrent2 = "Smoking status", 
                         paga = "Physical activity", imp_paga = "Physical activity*",
                         neoadj_treat = "Received neoadjuvant", 
                         imp_neoadj_treat = "Received neoadjuvant*", 
                         imp_debulking = "Debulking status*", 
                         NEW_dblkstat_treat_CA125 = "Debulking status", 
                         CCI_new = "CCI", CCI_new_Cat = "CCI categories",
                         imp_CCI_new_Cat = "CCI categories*",
                         aspirin = "Aspirin use",
                         aspirin_duration = "Aspirin duration (months)", 
                         aspirin_duration_cat = "Aspirin duration",
                         aspirin_duration_for_users = "Aspirin duration for users (months)",
                         aspirin_freq = "Aspirin frequency (Number of days per month)", 
                         aspirin_freq_cat = "Aspirin frequency",
                         aspirin_freq_for_users = "Aspirin frequency for users (Number of days per month)", 
                         aspirin_ind_init = "Aspirin indication (initial categories)",
                         aspirin_ind = "Aspirin indication",
                         nsaid = "Non-aspirin NSAID use", 
                         nsaid_duration = "Non-aspirin NSAID duration (months)", 
                         nsaid_duration_cat = "Non-aspirin NSAID duration",
                         nsaid_duration_for_users = "Non-aspirin NSAID duration for users (months)", 
                         nsaid_freq = "Non-aspirin NSAID frequency (Number of days per month)", 
                         nsaid_freq_cat = "Non-aspirin NSAID frequency",
                         nsaid_freq_for_users = "Non-aspirin NSAID frequency for users (Number of days per month)", 
                         nsaid_ind_init = "Non-aspirin NSAID indication (initial categories)",
                         nsaid_ind = "Non-aspirin NSAID indication",
                         aceta = "Acetaminophen use", 
                         acetaminophen_duration = "Acetaminophen duration (months)", 
                         acetaminophen_duration_cat = "Acetaminophen duration",
                         acetaminophen_duration_for_users = "Acetaminophen duration for users (months)", 
                         acetaminophen_freq = "Acetaminophen frequency (Number of days per month)", 
                         acetaminophen_freq_cat = "Acetaminophen frequency",
                         acetaminophen_freq_for_users = "Acetaminophen frequency for users (Number of days per month)", 
                         aceta_ind_init = "Acetaminophen indication (initial categories)",
                         aceta_ind = "Acetaminophen indication",
                         site_2 = "Study site")
```

# Drug overlap

```{r}
library(VennDiagram)

# venn.diagram(
#   x = list(c(analgesics$suid[analgesics$aceta == "Yes"]),
#            c(analgesics$suid[analgesics$nsaid == "Yes"]),
#            c(analgesics$suid[analgesics$aspirin == "Yes"])
#            ),
#   category.names = c("Acetaminophen",
#                      "Non-aspirin NSAIDs",
#                      "Aspirin"
#                      ),
#   filename = 'Figure S1.png',
#   output=TRUE,
#   disable.logging = TRUE,
# 
#   # Output features
#   imagetype="png" ,
#   height = 1000 ,
#   width = 1000 ,
#   resolution = 300,
#   compression = "lzw",
# 
#   # Circles
#   lwd = 2,
#   lty = 'blank',
#   fill = c(viridis::rocket(n = 3)),
#   margin = 0.22,
# 
#   # Categories
#   cat.fontfamily = "sans",
#   cat.cex = 0.8,
# 
#   # Numbers
#   cex = .6,
#   fontface = "bold",
#   fontfamily = "sans",
#   # cat.pos = c(-90, 0, 90), #
#   cat.dist = c(0.15, 0.15, 0.1), # aceta, nsaid, asp
#   # ext.percent = 2
#   #ext.percent = 5
# )
knitr::include_graphics(paste0(here::here(), '/Figure S1.png'))

```

AA comment   
at least at the “ever use” level to have “aspirin only,” “non aspirin NSAIDS only,” “Acetaminophen only,” and a “Mixed use” categories to put into a multiple regression model as an exploratory analysis.  Distinguishing current versus past here could also be helpful.

```{r overlap group coding}
analgesics1 <- analgesics %>% 
  mutate(aspirin_ever = case_when(
    aspirin == "No" &
      nsaid == "No" &
      aceta == "No"            ~ "Never analgesics",
    aspirin == "No"            ~ "Never aspirin but others",
    
    aspirin == "Yes" &
      nsaid == "No" &
      aceta == "No"            ~ "Aspirin only",
    aspirin == "Yes"           ~ "Aspirin + others",
    TRUE                       ~ "?"
  )) %>% 
  mutate(nsaid_ever = case_when(
    aspirin == "No" &
      nsaid == "No" &
      aceta == "No"            ~ "Never analgesics",
    nsaid == "No"              ~ "Never nsaid but others",
    
    aspirin == "No" &
      nsaid == "Yes" &
      aceta == "No"            ~ "NSAIDs only",
    nsaid == "Yes"             ~ "NSAIDs + others",
    TRUE                       ~ "?"
  )) %>% 
  mutate(aceta_ever = case_when(
    aspirin == "No" &
      nsaid == "No" &
      aceta == "No"            ~ "Never analgesics",
    aceta == "No"              ~ "Never aceta but others",
    
    aspirin == "No" &
      nsaid == "No" &
      aceta == "Yes"           ~ "Aceta only",
    aceta == "Yes"             ~ "Aceta + others",
    TRUE                       ~ "?"
  )) %>% 
  # mutate_at(c("aspirin_ever", "nsaid_ever", 
  #             "aceta_ever"),
  #           ~ as.character(.)) %>% 
  mutate_at(c("aspirin_ever", "nsaid_ever", 
              "aceta_ever"),
            ~ relevel(factor(.), ref = "Never analgesics")) #%>% 
  # mutate(nsaid_ever = factor(nsaid_ever, 
  #                            levels = c("Never analgesics",
  #                                       "nsaid +/- others",
  #                                       "Never nsaid but others"
  #                            )))
```


## never use of any analgesic medication, never use of aspirin but use of other analgesics, ever use of aspirin (Lauren)
```{r table ever}
analgesics1 %>% 
  select(aspirin_ever, nsaid_ever, aceta_ever) %>% 
  tbl_summary(
    statistic=list(all_continuous() ~ "{median} ({min}, {max})"
    )) %>% 
  bold_labels() %>% add_stat_label()
```


<!-- ```{r model ever} -->
<!-- model_1 <- coxph(Surv(time = analgesics1$os_time,  -->
<!--                    event = analgesics1$os_event) ~ aspirin_ever + nsaid_ever + aceta_ever + refage + site_2 + imp_stage, -->
<!--               data = analgesics1)  %>%  -->
<!--   tbl_regression(exponentiate = TRUE) %>%  -->
<!--   bold_labels() %>% italicize_levels() %>%  -->
<!--   bold_p(t = .05) %>%  -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") -->

<!-- model_2 <- coxph(Surv(time = analgesics1$os_time,  -->
<!--                       event = analgesics1$os_event) ~ aspirin_ever + nsaid_ever + aceta_ever + refage + site_2 + imp_stage +  -->
<!--                    imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance + -->
<!--                    imp_medicaid_insurance, -->
<!--                  data = analgesics1)  %>%  -->
<!--   tbl_regression(exponentiate = TRUE) %>%  -->
<!--   bold_p(t = .05) %>%  -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") -->

<!-- model_3 <- coxph(Surv(time = analgesics1$os_time,  -->
<!--                    event = analgesics1$os_event) ~ aspirin_ever + nsaid_ever + aceta_ever + refage + site_2 + imp_stage +  -->
<!--                   imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance + -->
<!--                    imp_medicaid_insurance +  -->
<!--                   imp_debulking, -->
<!--               data = analgesics1)  %>%  -->
<!--   tbl_regression(exponentiate = TRUE) %>%  -->
<!--   bold_p(t = .05) %>%  -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") -->

<!-- tbl_merge(list(model_1, model_2, model_3), tab_spanner = c("**Primary**", "**+ counfounders**", "**Fully adjusted**")) -->
<!-- ``` -->

## 3 independent "ever" models
```{r}
coxph(Surv(time = analgesics1$os_time, 
                   event = analgesics1$os_event) ~ aspirin_ever + refage + site_2 + imp_stage + 
                  imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance + 
                  imp_debulking,
              data = analgesics1)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
coxph(Surv(time = analgesics1$os_time, 
                   event = analgesics1$os_event) ~ nsaid_ever + refage + site_2 + imp_stage + 
                  imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance + 
                  imp_debulking,
              data = analgesics1)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
coxph(Surv(time = analgesics1$os_time, 
                   event = analgesics1$os_event) ~ aceta_ever + refage + site_2 + imp_stage + 
                  imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance + 
                  imp_debulking,
              data = analgesics1)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
```



## combined asp + nsaid
```{r}
analgesics2 <- analgesics %>% 
  mutate(all_nsaids_ever = case_when(
    aspirin == "No" &
      nsaid == "No" &
      aceta == "No"            ~ "Never analgesics",
    aspirin == "Yes" |
    nsaid == "Yes"             ~ "NSAIDs +/- others",
    aspirin == "No" &
    nsaid == "No"              ~ "Never NSAIDs but others",
    
    TRUE                       ~ "?"
  )) %>% 
  mutate(aceta_ever = case_when(
    aspirin == "No" &
      nsaid == "No" &
      aceta == "No"            ~ "Never analgesics",
    aceta == "No"              ~ "Never aceta but others",
    
    aceta == "Yes"             ~ "aceta +/- others",
    TRUE                       ~ "?"
  )) %>% 
  # mutate_at(c("aspirin_ever", "nsaid_ever", 
  #             "aceta_ever"),
  #           ~ as.character(.)) %>% 
  mutate_at(c("all_nsaids_ever", 
              "aceta_ever"),
            ~ relevel(factor(.), ref = "Never analgesics")) #%>% 
  # mutate(nsaid_ever = factor(nsaid_ever, 
  #                            levels = c("Never analgesics",
  #                                       "nsaid +/- others",
  #                                       "Never nsaid but others"
  #                            )))
```


```{r model all }
model_1 <- coxph(Surv(time = analgesics2$os_time, 
                   event = analgesics2$os_event) ~ all_nsaids_ever + aceta_ever + refage + site_2 + imp_stage,
              data = analgesics2)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_2 <- coxph(Surv(time = analgesics2$os_time, 
                      event = analgesics2$os_event) ~ all_nsaids_ever + aceta_ever + refage + site_2 + imp_stage + 
                   imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance,
                 data = analgesics2)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_3 <- coxph(Surv(time = analgesics2$os_time, 
                   event = analgesics2$os_event) ~ all_nsaids_ever + aceta_ever + refage + site_2 + imp_stage + 
                  imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance + 
                  imp_debulking,
              data = analgesics2)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

tbl_merge(list(model_1, model_2, model_3), tab_spanner = c("**Primary**", "**+ counfounders**", "**Fully adjusted**"))
```

## More facet
```{r}
analgesics3 <- analgesics %>% 
  mutate(combined_drugs = case_when(
    aspirin == "No" &
      nsaid == "No" &
      aceta == "No"            ~ "None",
    aspirin == "Yes" &
      nsaid == "Yes" &
      aceta == "Yes"            ~ "All",
    aspirin == "Yes" &
      nsaid == "No" &
      aceta == "No"            ~ "aspirin",
    aspirin == "No" &
      nsaid == "Yes" &
      aceta == "No"            ~ "NSAID",
    aspirin == "No" &
      nsaid == "No" &
      aceta == "Yes"            ~ "Aceta",
    TRUE                        ~ "All"
  )) %>% 
  mutate_at(c("combined_drugs"),
            ~ relevel(factor(.), ref = "None"))
```


```{r model separate}
model_1 <- coxph(Surv(time = analgesics3$os_time, 
                   event = analgesics3$os_event) ~ combined_drugs + refage + site_2 + imp_stage,
              data = analgesics3)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_2 <- coxph(Surv(time = analgesics3$os_time, 
                      event = analgesics3$os_event) ~ combined_drugs + refage + site_2 + imp_stage + 
                   imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance,
                 data = analgesics3)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_3 <- coxph(Surv(time = analgesics3$os_time, 
                   event = analgesics3$os_event) ~ combined_drugs + refage + site_2 + imp_stage + 
                  imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance + 
                  imp_debulking,
              data = analgesics3)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

tbl_merge(list(model_1, model_2, model_3), tab_spanner = c("**Primary**", "**+ counfounders**", "**Fully adjusted**"))
```

```{r}
analgesics4 <- analgesics %>% 
  mutate(combined_drugs2 = case_when(
    aspirin == "No" &
      nsaid == "No" &
      aceta == "No"            ~ "None",
    aspirin == "Yes" &
      nsaid == "Yes" &
      aceta == "Yes"            ~ "All",
    # aspirin == "Yes" &
    #   nsaid == "No" &
    #   aceta == "No"            ~ "aspirin",
    (aspirin == "Yes" |
      nsaid == "Yes") &
      aceta == "No"            ~ "asp +/-NSAID",
    aspirin == "No" &
      nsaid == "No" &
      aceta == "Yes"            ~ "Aceta",
    TRUE                        ~ "All"
  )) %>% 
  mutate_at(c("combined_drugs2"),
            ~ relevel(factor(.), ref = "None"))
```


```{r model all NSAIDs}
model_1 <- coxph(Surv(time = analgesics4$os_time, 
                   event = analgesics4$os_event) ~ combined_drugs2 + site_2 + imp_stage,
              data = analgesics4)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_2 <- coxph(Surv(time = analgesics4$os_time, 
                      event = analgesics4$os_event) ~ combined_drugs2 + refage + site_2 + imp_stage + 
                   imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance,
                 data = analgesics4)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_3 <- coxph(Surv(time = analgesics4$os_time, 
                   event = analgesics4$os_event) ~ combined_drugs2 + refage + site_2 + imp_stage + 
                  imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance + 
                  imp_debulking,
              data = analgesics4)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

tbl_merge(list(model_1, model_2, model_3), tab_spanner = c("**Primary**", "**+ counfounders**", "**Fully adjusted**"))
```


# Recency of use
```{r load recency}
analgesics <-
  read_rds(paste0(here::here(), "/analgesics data with recency 03062025.rds"))
```

```{r Labeling imputed data recency}
var_label(analgesics) <- list(refage = "Patient age", 
                         stage = "Clinical stage", 
                         histotype2 = "Histotype", 
                         BMI_recent_grp = "BMI categories", 
                         ins2 = "Insurance",
                         private_insurance = "Private insurance", 
                         medicare_insurance = "Medicare insurance",
                         medicaid_insurance = "Medicaid insurance",
                         NEW_dblkstat_treat_CA125 = "Debulking status", 
                         CCI_new = "CCI", CCI_new_Cat = "CCI categories",
                         site_2 = "Study site")
```

## Table
```{r}
analgesics %>% 
  select(aspirin_rec_cat : aceta_rec_cat) %>% 
  tbl_summary() %>% 
  bold_labels() %>% add_stat_label()
```

## HR
```{r}
coxph(Surv(time = analgesics$os_time, 
                   event = analgesics$os_event) ~ aspirin_rec_cat + nsaid_rec_cat + aceta_rec_cat +
                   refage + site_2 + stage + 
                strata(histotype2) +
                CCI_new_Cat + BMI_recent_grp + private_insurance + medicare_insurance +
                   medicaid_insurance + 
                  NEW_dblkstat_treat_CA125,
              data = analgesics)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
```












