---
title: "Manuscript analysis"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    toc_depth : 4
    theme: united
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type= "text/css">

. figure {
   margin-top: 25px;
   margin-bottom: 100px;
}

table {
    margin-top: 10px;
    margin-bottom: 25px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
```

```{r library}
library(here)
library(tidyverse)
library(labelled)
library(ggplot2)
library(ggforce)
library(gtsummary)
library(survminer)
library(survival)
library(adjustedCurves)
library(riskRegression)
theme_set(theme_classic())
theme_gtsummary_compact()
```

```{r load}
path <- fs::path("", "Volumes", "Peres_Research", "AACES2", "Analgesic medications and survival")
analgesics <-
  read_rds(paste0(here::here(), "/Cleaned imputed analgesics medication data_phase1 w income insurance education_05302024.rds")) %>% 
  rename(imp_debulking = imp_NEW_dblkstat_treat_CA125) %>% 
  mutate(os_years = os_time / 365.25)
```

```{r Labeling imputed data}
var_label(analgesics) <- list(refage = "Patient age", 
                         stage = "Clinical stage", imp_stage = "Clinical stage (imputed)", 
                         histotype2 = "Histotype", imp_histotype2 = "Histotype (imputed)", 
                         BMI_recent = "BMI (recent)", BMI_recent_grp = "BMI categories", 
                         imp_BMI_recent_grp = "BMI categories (imputed)", 
                         ins2 = "Insurance",
                         private_insurance = "Private insurance", 
                         imp_private_insurance = "Private insurance*", 
                         medicare_insurance = "Medicare insurance",
                         imp_medicare_insurance = "Medicare insurance*",
                         medicaid_insurance = "Medicaid insurance",
                         imp_medicaid_insurance = "Medicaid insurance*",
                         menopause = "Menopause", imp_menopause = "Menopause (imputed)",
                         education = "Education", imp_education = "Education (imputed)",
                         smokcurrent2 = "Smoking status", 
                         paga = "Physical activity", imp_paga = "Physical activity (imputed)",
                         neoadj_treat = "Received neoadjuvant", 
                         imp_neoadj_treat = "Received neoadjuvant (imputed)", 
                         imp_debulking = "Debulking status (imputed)", 
                         NEW_dblkstat_treat_CA125 = "Debulking status", 
                         CCI_new = "CCI", CCI_new_Cat = "CCI categories",
                         imp_CCI_new_Cat = "CCI categories (imputed)",
                         aspirin = "Aspirin use",
                         aspirin_duration = "Aspirin duration (months)", 
                         aspirin_duration_cat = "Aspirin duration (cat)",
                         aspirin_duration_for_users = "Aspirin duration for users (months)",
                         aspirin_freq = "Aspirin frequency (Number of days per month)", 
                         aspirin_freq_cat = "Aspirin frequency (cat)",
                         aspirin_freq_for_users = "Aspirin frequency for users (Number of days per month)", 
                         aspirin_ind_init = "Aspirin indication (initial categories)",
                         aspirin_ind = "Aspirin indication",
                         nsaid = "Non-aspirin NSAID use", 
                         nsaid_duration = "Non-aspirin NSAID duration (months)", 
                         nsaid_duration_cat = "Non-aspirin NSAID duration(cat)",
                         nsaid_duration_for_users = "Non-aspirin NSAID duration for users (months)", 
                         nsaid_freq = "Non-aspirin NSAID frequency (Number of days per month)", 
                         nsaid_freq_cat = "Non-aspirin NSAID frequency(cat)",
                         nsaid_freq_for_users = "Non-aspirin NSAID frequency for users (Number of days per month)", 
                         nsaid_ind_init = "Non-aspirin NSAID indication (initial categories)",
                         nsaid_ind = "Non-aspirin NSAID indication",
                         aceta = "Acetaminophen use", 
                         acetaminophen_duration = "Acetaminophen duration (months)", 
                         acetaminophen_duration_cat = "Acetaminophen duration (cat)",
                         acetaminophen_duration_for_users = "Acetaminophen duration for users (months)", 
                         acetaminophen_freq = "Acetaminophen frequency (Number of days per month)", 
                         acetaminophen_freq_cat = "Acetaminophen frequency (cat)",
                         acetaminophen_freq_for_users = "Acetaminophen frequency for users (Number of days per month)", 
                         aceta_ind_init = "Acetaminophen indication (initial categories)",
                         aceta_ind = "Acetaminophen indication",
                         site_2 = "Study site")
```

# I. Table S1. Clinical table
```{r Clinical table}
analgesics %>% 
  select(refage, stage, imp_stage, histotype, 
         histotype2, imp_histotype2, 
         BMI_recent, imp_BMI_recent_grp,
         menopause, imp_menopause, smokcurrent2, 
         neoadj_treat, imp_neoadj_treat, 
         NEW_dblkstat_treat_CA125, imp_debulking,
         CCI_new, CCI_new_Cat, imp_CCI_new_Cat,
         paga, imp_paga,
         income, imp_income, num_family,
         ins2,
         private_insurance, imp_private_insurance,
         medicare_insurance, imp_medicare_insurance,
         medicaid_insurance, imp_medicaid_insurance,
         education, imp_education, os_years, os_event) %>% 
  tbl_summary(type = list(
    c(neoadj_treat, imp_neoadj_treat,
      paga, imp_paga,
         private_insurance, imp_private_insurance,
         medicare_insurance, imp_medicare_insurance,
         medicaid_insurance, imp_medicaid_insurance) ~ "categorical"),
    statistic=list(all_continuous() ~ "{median} ({min}, {max})"
    )) %>% 
  bold_labels() %>% add_stat_label()
```

# II. Table S2. Tables by analgesics
```{r}
tbl1 <- analgesics %>% 
  select(refage, stage, imp_stage, histotype, 
         histotype2, imp_histotype2, 
         BMI_recent, imp_BMI_recent_grp,
         menopause, imp_menopause, smokcurrent2, 
         neoadj_treat, imp_neoadj_treat, 
         NEW_dblkstat_treat_CA125, imp_debulking,
         CCI_new, CCI_new_Cat, imp_CCI_new_Cat,
         paga, imp_paga,
         income, imp_income, num_family,
         ins2,
         private_insurance, imp_private_insurance,
         medicare_insurance, imp_medicare_insurance,
         medicaid_insurance, imp_medicaid_insurance,
         education, imp_education,
         aspirin, nsaid, aceta) %>% 
  tbl_summary(by = aspirin,
              type = list(
    c(nsaid, aceta,
      neoadj_treat, imp_neoadj_treat,
         private_insurance, imp_private_insurance,
         medicare_insurance, imp_medicare_insurance,
         medicaid_insurance, imp_medicaid_insurance) ~ "categorical"),
    statistic=list(all_continuous() ~ "{median} ({min}, {max})"
  )) %>% 
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% bold_p(t = 0.05)

tbl2 <- analgesics %>% 
  select(refage, stage, imp_stage, histotype, 
         histotype2, imp_histotype2, 
         BMI_recent, imp_BMI_recent_grp,
         menopause, imp_menopause, smokcurrent2, 
         neoadj_treat, imp_neoadj_treat, 
         NEW_dblkstat_treat_CA125, imp_debulking,
         CCI_new, CCI_new_Cat, imp_CCI_new_Cat,
         paga, imp_paga,
         income, imp_income, num_family,
         ins2,
         private_insurance, imp_private_insurance,
         medicare_insurance, imp_medicare_insurance,
         medicaid_insurance, imp_medicaid_insurance,
         education, imp_education,
         aspirin, nsaid, aceta) %>% 
  tbl_summary(by = nsaid,
              type = list(
    c(aspirin, aceta,
      neoadj_treat, imp_neoadj_treat,
         private_insurance, imp_private_insurance,
         medicare_insurance, imp_medicare_insurance,
         medicaid_insurance, imp_medicaid_insurance) ~ "categorical"),
    statistic=list(all_continuous() ~ "{median} ({min}, {max})"
  )) %>% 
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% bold_p(t = 0.05)

tbl3 <- analgesics %>% 
  select(refage, stage, imp_stage, histotype, 
         histotype2, imp_histotype2, 
         BMI_recent, imp_BMI_recent_grp,
         menopause, imp_menopause, smokcurrent2, 
         neoadj_treat, imp_neoadj_treat, 
         NEW_dblkstat_treat_CA125, imp_debulking,
         paga, imp_paga,
         income, imp_income, num_family,
         ins2,
         private_insurance, imp_private_insurance,
         medicare_insurance, imp_medicare_insurance,
         medicaid_insurance, imp_medicaid_insurance,
         education, imp_education,
         CCI_new, CCI_new_Cat, imp_CCI_new_Cat,
         aspirin, nsaid, aceta) %>% 
  tbl_summary(by = aceta,
              type = list(
    c(aspirin, nsaid,
      neoadj_treat, imp_neoadj_treat,
         private_insurance, imp_private_insurance,
         medicare_insurance, imp_medicare_insurance,
         medicaid_insurance, imp_medicaid_insurance) ~ "categorical"),
    statistic=list(all_continuous() ~ "{median} ({min}, {max})"
  )) %>% 
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% bold_p(t = 0.05)
```

```{r}
tbl_merge(list(tbl1, tbl2, tbl3), tab_spanner = c("**By Aspirin Use** (N = {N})",
                                                  "**By NSAID Use** (N = {N})",
                                                  "**By Acetaminophen Use** (N = {N})"))
```

# HR - Table 1 - Yes/no users - Imputed data

Model 1 - adjust for age, study site, imputed stage, and imputed histotype   
Model 2 - = 1 + imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance   
Model 3 - = 2 + imp_debulking   
```{r}
model_1 <- coxph(Surv(time = analgesics$os_time, 
                   event = analgesics$os_event) ~ aspirin + nsaid + aceta + refage + site_2 + imp_stage + 
                strata(imp_histotype2),
              data = analgesics)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_2 <- coxph(Surv(time = analgesics$os_time, 
                      event = analgesics$os_event) ~ aspirin + nsaid + aceta + refage + site_2 + imp_stage + 
                   strata(imp_histotype2) +
                   imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance,
                 data = analgesics)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_3 <- coxph(Surv(time = analgesics$os_time, 
                   event = analgesics$os_event) ~ aspirin + nsaid + aceta + refage + site_2 + imp_stage + 
                strata(imp_histotype2) + 
                  imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance + 
                  imp_debulking,
              data = analgesics)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

tbl_merge(list(model_1, model_2, model_3), tab_spanner = c("**Primary**", "**+ counfounders**", "**Fully adjusted**"))
```

PH assumption
```{r}
coxph(Surv(time = analgesics$os_time, 
                   event = analgesics$os_event) ~ aspirin + nsaid + aceta + refage + site_2 + imp_stage + 
                strata(imp_histotype2),
              data = analgesics) %>%
  cox.zph()
coxph(Surv(time = analgesics$os_time, 
                      event = analgesics$os_event) ~ aspirin + nsaid + aceta + refage + site_2 + imp_stage + 
                   strata(imp_histotype2) +
                   imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance,
                 data = analgesics) %>%
  cox.zph()
coxph(Surv(time = analgesics$os_time, 
                   event = analgesics$os_event) ~ aspirin + nsaid + aceta + refage + site_2 + imp_stage + 
                strata(imp_histotype2) + 
                  imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance + 
                  imp_debulking,
              data = analgesics) %>%
  cox.zph()
```

# HR - Table 2 - cut-points - Imputed data

Model 1 - adjust for age, study site, imputed stage, and imputed histotype   
Model 2 - = 1 + imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance   
Model 3 - = 2 + imp_debulking   
```{r}
model_1 <- coxph(Surv(time = analgesics$os_time, 
                   event = analgesics$os_event) ~ aspirin_duration_cat + nsaid_duration_cat + acetaminophen_duration_cat + 
                refage + site_2 + imp_stage + strata(imp_histotype2),
              data = analgesics)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_2 <- coxph(Surv(time = analgesics$os_time, 
                   event = analgesics$os_event) ~ aspirin_duration_cat + nsaid_duration_cat + acetaminophen_duration_cat +
                refage + site_2 + imp_stage + strata(imp_histotype2) + 
                imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance,
              data = analgesics)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_3 <- coxph(Surv(time = analgesics$os_time, 
                   event = analgesics$os_event) ~ aspirin_duration_cat + nsaid_duration_cat + acetaminophen_duration_cat +
                refage + site_2 + imp_stage + strata(imp_histotype2) + 
                imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance + 
                  imp_debulking,
              data = analgesics)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

tbl_duration <- tbl_merge(list(model_1, model_2, model_3), 
                          tab_spanner = c("**Primary**", "**+ counfounders**", "**Fully adjusted**"))


model_1 <- coxph(Surv(time = analgesics$os_time, 
                   event = analgesics$os_event) ~ aspirin_freq_cat + nsaid_freq_cat + acetaminophen_freq_cat + 
                refage + site_2 + imp_stage + strata(imp_histotype2),
              data = analgesics)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_2 <- coxph(Surv(time = analgesics$os_time, 
                   event = analgesics$os_event) ~ aspirin_freq_cat + nsaid_freq_cat + acetaminophen_freq_cat + 
                refage + site_2 + imp_stage + strata(imp_histotype2) + 
                imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance,
              data = analgesics)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

model_3 <- coxph(Surv(time = analgesics$os_time, 
                   event = analgesics$os_event) ~ aspirin_freq_cat + nsaid_freq_cat + acetaminophen_freq_cat + 
                refage + site_2 + imp_stage + strata(imp_histotype2) + 
                imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance + 
                  imp_debulking,
              data = analgesics)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

tbl_frequency <- tbl_merge(list(model_1, model_2, model_3), 
                           tab_spanner = c("**Primary**", "**+ counfounders**", "**Fully adjusted**"))

tbl_stack(list(tbl_duration, tbl_frequency), 
          group_header = c("Duration cut-points", "Frequency cut-points"))

```

<!-- # test -->
<!-- ```{r} -->
<!-- coxph(Surv(time = analgesics$os_time,  -->
<!--                    event = analgesics$os_event) ~ aspirin_freq_cat + nsaid_freq_cat + acetaminophen_freq_cat +  -->
<!--                 refage + site_2 + imp_stage + strata(imp_histotype2) +  -->
<!--                 imp_CCI_new_Cat + imp_BMI_recent_grp + imp_insurance +  -->
<!--                   imp_debulking, -->
<!--               data = analgesics)  %>%  -->
<!--   tbl_regression(exponentiate = TRUE) %>%  -->
<!--   bold_p(t = .05) %>%  -->
<!--   add_nevent(location = "level") %>%  -->
<!--   add_n(location = "level") -->

<!-- coxph(Surv(time = analgesics$os_time,  -->
<!--                    event = analgesics$os_event) ~ aspirin_freq_cat + nsaid_freq_cat + acetaminophen_freq_cat +  -->
<!--                 refage + site_2 + imp_stage + strata(imp_histotype2) +  -->
<!--                 imp_CCI_new_Cat + imp_BMI_recent_grp + imp_insurance +  -->
<!--                   imp_debulking, -->
<!--               data = analgesics)  %>%  -->
<!--   tbl_regression(exponentiate = TRUE) %>%  -->
<!--   bold_p(t = .05) %>%  -->
<!--   add_nevent(location = "level") %>%  -->
<!--   add_n(location = "level") %>% -->
<!--   # merge the colums into a single column -->
<!--   modify_cols_merge( -->
<!--     pattern = "{stat_nevent} ({stat_n})", -->
<!--     rows = !is.na(stat_nevent) -->
<!--   ) %>% -->
<!--   # update header to event rate -->
<!--   modify_header(stat_nevent = "**N (Event N)**") %>% -->

<!--   # merge the colums into a single column -->
<!--   modify_cols_merge( -->
<!--     pattern = "{estimate} ({ci})", -->
<!--     rows = !is.na(estimate) -->
<!--   ) %>% -->
<!--   # update header to event rate -->
<!--   modify_header(estimate = "**HR (95% CI)**") -->
<!-- ``` -->









# HR - Table S3 - Indication

Model 2 - + indication  
```{r}
indication <- analgesics #%>% 
  # select(suid, aspirin, starts_with("aspirin_ind")) %>%
  # mutate(aspirin_heart_ind = case_when(
  #   aspirin_ind == "Heart disease prevention"    ~ "Yes",
  #   !is.na(aspirin_ind)                          ~ "No"
  # )) %>% 
  # mutate(aspirin_other_ind = case_when(
  #   aspirin_ind == "Other uses"                  ~ "Yes",
  #   !is.na(aspirin_ind)                          ~ "No"
  # )) %>% 
  # mutate_at(c("aspirin_heart_ind", "aspirin_other_ind"),
  #           ~ factor(., levels = c("No",
  #                                  "Yes")))

coxph(Surv(time = indication$os_time, 
           event = indication$os_event) ~ aspirin_ind + nsaid + aceta +
        refage + site_2 + imp_stage + 
        strata(imp_histotype2)+ 
        # imp_CCI_new_Cat +
        imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance + 
        imp_debulking,
      data = indication)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>%
  add_n(location = "level")
```

# HR - Table S4 - complete case model
```{r}
coxph(Surv(time = analgesics$os_time, 
                   event = analgesics$os_event) ~ aspirin + nsaid + aceta + refage + site_2 + stage + 
                strata(histotype2) +
                CCI_new_Cat + BMI_recent_grp + private_insurance + medicare_insurance +
                   medicaid_insurance,
              data = analgesics)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
```

# Figure - adjusted KM - with imputed data
A - Aspirin  
B - NSAIDs   
C - Aceta
```{r, fig.height=9, fig.width=5}
analgesics_data_frame <- analgesics %>%
  mutate(os_time = os_time / 30.417) %>% 
  as.data.frame()

coxph(Surv(time = analgesics_data_frame$os_time, 
             event = analgesics_data_frame$os_event) ~ aspirin + nsaid + aceta + refage + site_2 + imp_stage + 
          strata(imp_histotype2) + 
          imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance + 
          imp_debulking,
        data = analgesics_data_frame)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

fit <- 
  coxph(Surv(time = analgesics_data_frame$os_time, 
             event = analgesics_data_frame$os_event) ~ aspirin + nsaid + aceta + refage + site_2 + imp_stage + 
          strata(imp_histotype2) + 
          imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance + 
          imp_debulking,
        data = analgesics_data_frame)


fig1a <-
  ggadjustedcurves(fit, data = analgesics_data_frame, 
                 # method = "single",
                 variable = "aspirin",
                 # font.legend = c(16, "black"),
                 legend.title = "",
                 palette = c("blue", "red"),
                 # xlim = c(0, 85)
                 xlab = "Time (months)",
                 ggtheme = theme_survminer()
                 )
fig1b <- ggadjustedcurves(fit, data = analgesics_data_frame, 
                 # method = "average", 
                 variable = "nsaid",
                 # font.legend = c(16, "black"),
                 legend.title = "",
                 palette = c("blue", "red"),
                 # xlim = c(0, 85)
                 xlab = "Time (months)",
                 ggtheme = theme_survminer()
                 )
fig1c <- ggadjustedcurves(fit, data = analgesics_data_frame, 
                 # method = "average", 
                 variable = "aceta",
                 # font.legend = c(16, "black"),
                 legend.title = "",
                 palette = c("blue", "red"),
                 # xlim = c(0, 85)
                 xlab = "Time (months)",
                 ggtheme = theme_survminer()
                 )

library(patchwork)
fig1a / fig1b / fig1c +
  plot_annotation(tag_levels = 'A')

ggsave("Figure 1 updated with model including 3 insurances variables_no method_02072025.pdf",
       width = 4,
       height = 10,
       dpi = 600)
```

```{r adjustedCurves}
analgesics_data_frame <- analgesics %>%
  mutate(os_time = os_time / 30.417)# %>% 
  # as.data.frame()

outcome_model <- survival::coxph(Surv(os_time, os_event) ~ aspirin + nsaid + aceta + refage + site_2 + imp_stage + 
          strata(imp_histotype2) +
          imp_CCI_new_Cat + imp_BMI_recent_grp + imp_private_insurance + imp_medicare_insurance +
                   imp_medicaid_insurance +
          imp_debulking,
        data = analgesics_data_frame, x=TRUE)

adjsurv_aspirin <- adjustedsurv(data = analgesics_data_frame,
                        variable = "aspirin",
                        ev_time = "os_time",
                        event = "os_event",
                        method = "direct",
                        outcome_model = outcome_model,
                        conf_int = TRUE)

fig1a <- plot(adjsurv_aspirin, 
              legend.title = NULL,legend.position = "top",
              xlab="Time (months)",
              custom_colors = c("blue", "red"),
              ylim = c(0,1))

adjsurv_nsaid <- adjustedsurv(data = analgesics_data_frame,
                        variable = "nsaid",
                        ev_time = "os_time",
                        event = "os_event",
                        method = "direct",
                        outcome_model = outcome_model,
                        conf_int = TRUE)

fig1b <- plot(adjsurv_nsaid, 
              legend.title = NULL,legend.position = "top",
              xlab="Time (months)",
              custom_colors = c("blue", "red"),
              ylim = c(0,1))

adjsurv_aceta <- adjustedsurv(data = analgesics_data_frame,
                        variable = "aceta",
                        ev_time = "os_time",
                        event = "os_event",
                        method = "direct",
                        outcome_model = outcome_model,
                        conf_int = TRUE)

fig1c <- plot(adjsurv_aceta, 
              legend.title = NULL,legend.position = "top",
               xlab="Time (months)",
             custom_colors = c("blue", "red"),
              ylim = c(0,1))


library(patchwork)
fig1a / fig1b / fig1c +
  plot_annotation(tag_levels = 'A')

ggsave("Figure 1 using adjustedCurves_02132025.pdf",
       width = 4,
       height = 10,
       dpi = 600)
```
























